\documentclass[]{resume-openfont}

\pagestyle{fancy}
\resetHeaderAndFooter
%--------------------------------------------------------------
% Convenience command - make it easy to fill template

% Create job position command. Parameters: company, position, location, when
\newcommand{\resumeHeading}[4]{\runsubsection{\uppercase{#1}}\descript{ | #2}\hfill\location{#3 | #4}\fakeNewLine}

% Create education heading. Parameters: Name, degree, location, when
\newcommand{\educationHeading}[4]{\runsubsection{#1}\hspace*{\fill}  \location{#3 | #4}\\
\descript{#2}\fakeNewLine}

% Parameters: courses
\newcommand{\courseWork}[1]{\textbf{Coursework:} #1}

% Parameters: courses
\newcommand{\teacherAssistant}[1]{\textbf{Teacher Assistant (TA):} #1}
 
%--------------------------------------------------------------
\begin{document}

%--------------------------------------------------------------
%     Profile
%--------------------------------------------------------------
\newcommand{\yourName}{Manan Sharma}
\newcommand{\yourEmail}{manan180796@gmail.com}
\newcommand{\yourPhone}{+919711306818}
\newcommand{\githubUserName}{sageprogrammer}
\newcommand{\linkedInUserName}{manan-sh}

% \alignProfileTable
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%     \ralewayBold{\href{\yourWebsite}{\Large \yourName}} & 
%     Email : \href{mailto:\yourEmail}{\yourEmail}
%     \\
%     \href{https://github.com/\githubUserName}{GitHub://\githubUserName} & 
%     Mobile : \yourPhone
%     \\
%     \href{https://www.linkedin.com/in/\linkedInUserName}{LinkedIn://\linkedInUserName} & Website : \href{\yourWebsite}{abdullaharif.tech}
%     \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape \yourName} \\ \vspace{1pt}
    \small \yourPhone $|$ \href{mailto:\yourEmail}{\underline{\yourEmail}} $|$ 
    \href{https://linkedin.com/in/\linkedInUserName}{\underline{linkedIn/\linkedInUserName}} $|$
    \href{https://github.com/\githubUserName}{\underline{github/\githubUserName}}
\end{center}


%--------------------------------------------------------------
%     Experience
%--------------------------------------------------------------
\section{Work Experience}
\resumeHeading{Summer of BitCoin}{Open Source}{}{Jul 2021 – Current}
\begin{tightemize}
    \item Implemented Taproot support for NBXplorer \& BTCPayServer, which is the next major upgrade after SegWit.
    \item Used ASP.Net framework with xunit testing.
    \item Used Dockers for stable testing envroments.
    \item Learned \& Implemented different BlockChain \& Signature concepts
\end{tightemize}
\sectionsep
\resumeHeading{Microsoft Research \& Development}{Data Science Intern}{Hyderabad, India}{May 2019 – Jul 2019}
\begin{tightemize}q
    \item Developed an Automated Question Answering System for Local Search in Bing.
    \item Trained our own Question \& Answer embeddings using BERT.
    \item Matched the Question and their Answers using closest embeddings.
\end{tightemize}
\sectionsep
\resumeHeading{Fabulyst}{Intern}{}{Aug 2016 - Nov 2016}
\begin{tightemize}
    \item Scrap different fashion items and their details from on-line resources and used MongoDB for storage. 
    \item Built an annotation tool for annotating tags for all the scraped items using AngularJS.
\end{tightemize}
\sectionsep


%--------------------------------------------------------------
%     Education
%--------------------------------------------------------------
\section{Education}
% Swap degree and school if your school is reputable
\educationHeading{International Institute of Information Technology, Hyderabad}{BTech \& MS By Research in Computer Science}{Hyderabad, India}{Jul 2016 - Jun 2022}
\sectionsep

\resumeHeading{Research}{}{}{Aug 2020 - Current}
\begin{tightemize}
    \item Working on Knowledge Completion in Knowledge Graph
    \item Knowledge Graph Relation extraction using Adversarial Techniques.
\end{tightemize}
\sectionsep
\resumeHeading{Teaching Assistant}{Topics in Applied Optimization}{}{Aug 2018-Nov 2018}

\sectionsep
\resumeHeading{Center For Visual Information Technology}{Research Assistant}{}{Aug 2016 - Nov 2019}
\begin{tightemize}
    \item Researched under Dr. Avinash Sharma.
    \item Reconstructing a 3D dynamic model via video feeds coming a uncalibrated camera setup.
\end{tightemize}
\educationHeading{Jaypee Institute of Information Technology, Noida}{BTech \& MTech in Computer Science}{Hyderabad, India}{Jul 2014 - Jun 2016}
\sectionsep
\sectionsep
\courseWork{Data Structures and Algorithms; Operating Systems; Complexity and Advanced Algorithms; Digital Image Processing; Statistical Methods in AI; Computer Vision; Optimization Methods; Introduction to Parallel Scientific Computing;Database Systems;Linear Algebra; Distributing Trust \& Blockchains; Compilers; Distributed Systems}
\sectionsep

%--------------------------------------------------------------
%     Achievments
%--------------------------------------------------------------
\section{Achivements}
\resumeHeading{Kickstart}{}{}{}
\begin{tightemize}
    \item Ranked 100 in Google Kick Start Round D 2019 in ~10000
    \item Ranked 581 in Google Kick Start Round D 2020 in ~10000
    \item Ranked 862 in Google Kick Start Round D 2021 in ~10000
\end{tightemize}
\resumeHeading{CodeChef}{}{}{}
\begin{tightemize}
    \item \textbf{Global Rank 1} in May Challenge 2021
\end{tightemize}
\sectionsep
\sectionsep
\resumeHeading{ACM-ICPC}{}{}{}
\begin{tightemize}
    \item 2017:Ranked 42 all over India in the On-site Coding Round at Asia Chennai Regional
    \item 2016:Ranked 99 all over India in the On-site Coding Round at Asia Amritapuri Regionals
\end{tightemize}
\resumeHeading{Miscellaneous}{}{}{}
\begin{tightemize}
    \item Qualified for Code Jam Round 2
    \item Qualified for HackerCup Round 2
\end{tightemize}

%--------------------------------------------------------------
%     Projects
%--------------------------------------------------------------
\section{Projects}
\Project{Ublas Matrix Library with Expresion Templates}{https://github.com/sageprogrammer/ublas/tree/develop/include/boost/numeric/ublas/matrix}
\descript{ C++, UBLAS, Linear Algebra}\\
\begin{tightemize}
    \item Created a Matrix Library in C++ using expression templates for compile time evaluation.
    \item The operations were written to support slicing a splicing without any verbose syntax.
\end{tightemize}

\Project{DECAFF Compiler}{https://github.com/Compilers-Monsoon2018-IIITH/decaff-compiler-manan180796}
\descript{C++,LLVM,YACC}\\
\begin{tightemize}
    \item Build a Compiler for a turing complete programming language Decaff.
    \item We used Bison and Yacc for parsing the language.
    \item To make the project modularized we used Visitor Patterns and many more OOPs techniques.
\end{tightemize}
\sectionsep
  
\Project{Parallel Image Compression using PCA}{https://github.comsageprogrammer/PCA-Image-Compression}
\descript{C++, OpenMP}\hfill \\
\begin{tightemize}
    \item Compress a given image using PCA.
    \item Create our own algorithm to compress image using PCA.
    \item Accelerate the compression time by parallizing the algorithm using openMP.
\end{tightemize}
\sectionsep

\Project{Russian Tweet Troll Analysis}{https://github.com/AakashKT/PSOSMProject}
\descript{Python, NLP} \\
\begin{tightemize}
    \item Build a Tweet analyzer if it is a troll or not.
    \item Trained our BERT model using russian troll dataset .
    \item Developed a frontend website for easy presentation
\end{tightemize}
\sectionsep


\Project{Student Teacher Transfer Learning}{https://github.com/sageprogrammer/student-teacher-transfer-learning}
\descript{Python, Pytorch, Tranfer Learning} \\
\begin{tightemize}
    \item Transfer the knowledge learned by very deep Neural Network to a shallower Neural Network.
    \item Train the original deep Neural Network on the original data.
    \item Make the learning faster for the smaller neural network via providing the soft targets.
\end{tightemize}
\sectionsep

\Project{Image Uncrop}{ https://github.com/sageprogrammer/CV-project }
\descript{Python, MRF, Computer Vision}\\
\begin{tightemize}
    \item Extend a given image using existing wild images on the internet.
    \item The images are positioned using Structure from Motion.
    \item The images are then stitched together seamlessly using Markovian Random Fields.
\end{tightemize}
 
\sectionsep

\Project{UNIX/Linux Shell}{https://github.com/sageprogrammer/Custom-Shell}
\descript{ C, Posix, OS}\\

Create a shell to simulate built-in commands,piping ,I/O redirection \& signals.
\sectionsep

\Project{Graphics}{}
\descript{ C++, JS, OpenGL, WebGL}\\
\begin{tightemize}
    \item Create a Bloxorz like game using OpenGL.
    \item Create a Fish Aquarium Simulator using WebGL.
    \item Created our own 3D movie.
\end{tightemize}
\sectionsep


%--------------------------------------------------------------
%     Skills
%--------------------------------------------------------------
\section{Skills}
\begin{resumeSkillList}
    \singleItem{Languages:}{Java, C++, C, Python, C\#, PHP, Bash, C, SQL}
    \\
    \singleItem{Web Development:}{AngularJS, JavaScript, TypeScript, HTML/CSS}
    \\
    \singleItem{Technology:}{Git, Docker, Unity,  \LaTeX, MongoDB, Neo4j, OpenMP, OpenGL, WebGL}
\end{resumeSkillList}

 % A more concise alternate 
% \begin{resumeSkillList}
%     \doubleItem{Languages:}{Java, C++, Python, C\#, PHP, Prolog, Bash, C, Racket}%
%     {Databases:}{SQL, MongoDB, Neo4j, DynamoDB}
%     \\
%     \doubleItem{Web Development:}{JavaScript, TypeScript, React, HTML/CSS}
%     {Technology:}{Git, AWS, GCP, Azure, Docker, \LaTeX}%
% \end{resumeSkillList}
\end{document}